Hydrodynamics of a Semipermeable Inextensible Membrane Under Flow and Confinement

### 2021-05-20 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex

\textcolor{magenta}{
%In our model, the permeating flux of viscous solvent is proportional to the normal component of membrane forces.
%which is equal to the jump in hydrodynamic pressure in our simulations with no viscosity contrast
%between interior and exterior fluids. 
For each of the cases in \S~\ref{sec:free_space} and \ref{sec:confinement}, 
we examine the contribution of the permeating flux from membrane tension and membrane bending forces. In free space, we find that both membrane forces contribute comparably in the simulations. As the vesicle hydrodynamics reaches an equilibrium, the two contributions add to zero as the permeating flux integrates to zero rate of change of the reduced area.
Under strong confinement, however, we find the membrane tension to contribute much more to the permeating flux than the membrane bending. For a vesicle going through a closely-fit channel the maximum flow velocity is $U_{max}=1000$ $\mu$m/s is chosen to match the experimental conditions. Such a large flow velocity contributes to large membrane tension, and thus reducing the time scale for change in water content. For a vesicle going through a contracting channel, we used a smaller $U_{max}$ than in the experiments (where the three-dimensional channel contracts in both cross-stream directions) to examine the effect of membrane permeability. We find that, due to the strong confinement, the membrane tension still dominates the membrane bending in contributing to the permeating flux as in the closely-fit channel.
}

>>>>

\textcolor{magenta}{
%In our model, the permeating flux of viscous solvent is proportional to the normal component of membrane forces.
%which is equal to the jump in hydrodynamic pressure in our simulations with no viscosity contrast
%between interior and exterior fluids. 
For each of the cases in \S~\ref{sec:free_space} and
\S~\ref{sec:confinement}, we examine the contribution of the permeating
flux from membrane tension and membrane bending forces. In free space,
we find that both membrane forces contribute comparably in the
simulations. As the vesicle hydrodynamics reaches an equilibrium, the
two contributions add to zero as the permeating flux integrates to zero
rate of change of the reduced area.  Under strong confinement, however,
we find the membrane tension to contribute much more to the permeating
flux than the membrane bending. For a vesicle going through a
closely-fit channel the maximum flow velocity is $U_{\max}=1000$
$\mu$m/s is chosen to match the experimental conditions. Such a large
flow velocity contributes to large membrane tension, and thus reducing
the time scale for change in water content. For a vesicle going through
a contracting channel, we used a smaller $U_{\max}$ than in the
experiments (where the three-dimensional channel contracts in both
cross-stream directions) to examine the effect of membrane permeability.
We find that, due to the strong confinement, the membrane tension still
dominates the membrane bending in contributing to the permeating flux as
in the closely-fit channel.
}
